Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-10-01 manuscript/ERL_global_C_review.Rmd
reduced file size for submission
https://github.com/forc-db/ERL-review/issues/55

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Tropical broadleaf MATURE.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate broadleaf MATURE.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate conifer MATURE.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Boreal conifer MATURE.png"))
```
\elandscape

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Flux_age_trends.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Stock_age_trends.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Tropical broadleaf YOUNG.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate broadleaf YOUNG.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate conifer YOUNG.png"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Boreal conifer YOUNG.png"))
```
\elandscape

>>>>

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Tropical broadleaf MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate broadleaf MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate conifer MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Boreal conifer MATURE.jpeg"))
```
\elandscape

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Flux_age_trends.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Stock_age_trends.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Tropical broadleaf YOUNG.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate broadleaf YOUNG.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate conifer YOUNG.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Boreal conifer YOUNG.jpeg"))
```
\elandscape
